MINOS Handover Plots

### 2024-03-21 minos/outcomes/QALY_comparison2.Rmd

```{r}
experiment <- params$experiment
baseline <- params$base
ints <- params$intervention
#intervention2 <- params$intervention2
start.year <- params$start.year
# # 
# experiment <- 'glasgow_scaled'
# baseline <- 'baseline'
# ints <- c('50All', '50UniversalCredit')
# start.year <- 2020
```

@@

```{r}
# QALY_comparison(base = base,
#                 base.name = baseline,
#                 int = int,
#                 int.name = intervention)

QALY_comparison(combined, ints)
```

>>>>

```{r}
experiment <- params$experiment
baseline <- params$base
ints <- params$intervention
start.year <- params$start.year
# #
# experiment <- 'arc_batch_10'
# baseline <- 'baseline'
# ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
# start.year <- 2020
```

@@

```{r}
QALY_comparison(combined, ints)
```

### 2024-03-21 minos/validation/handovers.Rmd

---
title: "MINOS Handover Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
handover_boxplots(raw.dat, base.dat, 'council_tax')
handover_lineplots(raw.dat, base.dat, "council_tax")
```

@@

@@

@@

>>>>

---

title: "MINOS Handover Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
```

@@

### Income Inequality

```{r}
handover_inequality_80_20(raw.dat, base.dat, var = 'hh_income')
```

@@

### Inequality

```{r}
handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_MCS')
```

@@

### Inequality

```{r}
handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_PCS')
```
